### 2021-07-19 doc/thesis/chapters/system-design-process.tex
system model

>>>>

Based on the previous steps, a model for the system is developed here.
This includes a process model, that is used for stragetic planning towards cost reduction, optimization of the implementation effort, or the schedule of subprojects, and a product model, which supports trade-offs and the identification of risks, or helps to explain the system as a whole.\\

Typically, a coarse model is created for almost all alternative designs that were found in the previous step.
A more detailed model is developed for the single, selected design.
The model itself may be represented in many different ways, such as state machines, block diagrams, flow diagrams, simulations or object-oriented diagrams.
